Verifying Demonstrations

### 2017-10-09 SystemModel.tex
Syncs notation of system model with protocol

\begin{frame}
\begin{definition}[Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((id, t, l)\) where
  \(id\in \Z_{2^\lambda}\) is an identifier,
  \(t = \interval{t_s}{t_e}\subseteq \R\) is a time interval and
  \(l = N_\epsilon(x, y)\subseteq \R^2\) is the location (an 
  \(\epsilon\)-neighbourhood of \((x,y)\)).
  A \emph{protest} is a set of subprotests sharing the same \(id\).
\end{definition}
\end{frame}

@@

\begin{frame}
\begin{definition}[Witness]
  A \emph{witness} \(w = (pid, id, t, l, wid)\) is a tuple where
  \(id, t, l\) are as in \cref{DefProtest},
  \(pid\) uniquely identifies the protester and \(wid\) uniquely identifies the 
  person who issued the witness.
  We let \(W\) be the set of all witnesses.
\end{definition}
\end{frame}

@@

\begin{frame}
\begin{definition}[Participation proof]
  A \emph{participation proof} of protester \(i\) participating in protest \(j\) 
  is the set
  \begin{align}
    \nonumber
    p_{i, j} =
    \left\{ (pid, id, t, l, wid)\in W \mid
    %\right. &
    pid = i, id = j,
    %\\ & \left.
    t \subseteq t_j, l\subseteq l_j \right\},
  \end{align}
  of all witnesses with the same protester and protest identifiers, witness time 
  interval \(t\) and location \(l\) is within those of the protest \(j\) (i.e.\ 
  \(t_j\) and \(l_j\)).
\end{definition}
\end{frame}

We can now define the participation count as follows.
\begin{frame}
\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(id\) as the 
  cardinality \(|P_{id}^{s,\theta}|\) of the set of participation proofs \[
    P_{id}^{s,\theta} = \left\{ p_{i,j} \mid
      j = id, s(p_{i,j})\geq \theta \right\}
  \] for some strength function \(s\colon \powerset(W)\to \R_+\) and a threshold 
  \(\theta\).
\end{definition}

>>>>

\begin{frame}
\begin{definition}[Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((cid, t, l)\) where
  \(cid\in \Z_{2^\lambda}\) is the cause\footnote{%
    I.e.\ the cause of the protest.
  } identifier,
  \(t = \interval{t_s}{t_e}\subseteq \R\) is a time interval and
  \(l = N_\epsilon(x, y)\subseteq \R^2\) is the location (an 
  \(\epsilon\)-neighbourhood of \((x,y)\)).
  A \emph{protest} is a set of subprotests sharing the same \(id\).
\end{definition}
\end{frame}

@@

\begin{frame}
\begin{definition}[Witness]
  A \emph{witness} \(w = (pid, cid, t, l, wid)\) is a tuple where
  \(cid, t, l\) are as in \cref{DefProtest},
  \(pid\) uniquely identifies the protester and \(wid\) uniquely identifies the 
  person who issued the witness.
  We let \(W\) be the set of all witnesses.
\end{definition}
\end{frame}

@@

\begin{frame}
\begin{definition}[Participation proof]
  A \emph{participation proof} of protester \(i\) participating in protest \(j\) 
  is the set
  \begin{align}
    \nonumber
    p_{i, j} =
    \left\{ (pid, cid, t, l, wid)\in W \mid
    %\right. &
    pid = i, cid = j,
    %\\ & \left.
    t \subseteq t_j, l\subseteq l_j \right\},
  \end{align}
  of all witnesses with the same protester and protest identifiers, witness time 
  interval \(t\) and location \(l\) is within those of the protest \(j\) (i.e.\ 
  \(t_j\) and \(l_j\)).
\end{definition}
\end{frame}

We can now define the participation count as follows.
\begin{frame}
\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(cid\) as the 
  cardinality \(|P_{cid}^{s,\theta}|\) of the set of participation proofs \[
    P_{cid}^{s,\theta} = \left\{ p_{i,j} \mid
      j = cid, s(p_{i,j})\geq \theta \right\}
  \] for some strength function \(s\colon \powerset(W)\to \R_+\) and a threshold 
  \(\theta\).
\end{definition}
